preparation

### 2025-03-10 data/preparation_2.Rmd
updated data prep

@@

```{r recoding}
youtube <- youtube %>% 
  mutate(
    across(c(`homophily_appear_1`, `homophily_appear_2`, `homophily_appear_3`, `homophily_appear_4`, `homophily_appear_5`, `homophily_behave_1`, `homophily_behave_2`, `homophily_behave_3`, `homophily_behave_4`, `homophily_behave_6`, parasocial_1, parasocial_2, parasocial_3, parasocial_4, parasocial_5),
           ~ recode (.,
             "Really disagree" = 1,
             "Disagree" = 2,
             "I don't know" = 3,
             "Agree" = 4,
             "Really agree" = 5
           ))) %>% 
  mutate(
    across(c(malleable_1, malleable_2, malleable_3, malleable_4, regularities_1, regularities_2, regularities_3, regularities_4, regularities_5, regularities_6, regularities_7),
           ~ recode(.,
             "Really disagree" = 1,
             "Disagree" = 2,
             "Neither agree nor disagree" = 3,
             "Agree" = 4,
             "Really agree" = 5
           ))) %>%  
  select(-c(homophily_behave_5))
```

@@

```{r age}
# calculating child age
date_today <- Sys.Date()  
youtube <- youtube %>% 
  mutate(bday = as.Date(bday, format = "%m/%d/%Y")) %>% 
  mutate(age = age_calc(
    bday,
    date_today,
    units = "years"
  ))
```

@@

# Parasocial relationship scores (each block separately, then aggregate)
youtube <- youtube %>% 
  # homophily-appear -- total possible score = 20
  mutate(h_appear_score = rowSums(across(`homophily-appear_1`:`homophily-appear_5`))) %>% 
  # homophily-behave -- total possible score = 20
  mutate(h_behave_score = rowSums(across(`homophily-behave_1`:`homophily-behave_6`))) %>% 
  # parasocial -- total possible score = 20
  mutate(parasocial_score = rowSums(across(parasocial_1:parasocial_5))) %>% 
  #Composite scores
  mutate(composite = rowSums(across(h_appear_score:parasocial_score))) %>% 
  # Proportion scores
  mutate(h_appear_score = h_appear_score/20) %>%
  mutate(h_behave_score = h_behave_score/20) %>%
  mutate(parasocial_score = parasocial_score/20) %>%
  mutate(composite = composite/60)

# Racial regularities score (behavior) -- total possible score = 35
youtube <- youtube %>% 
  # Reverse coded items
  mutate(across(c(behavior_3, behavior_5, behavior_7), ~ 6 - .)) %>% 
  # Score
  mutate(regularity_score = rowSums(across(behavior_1:behavior_7))) %>% 
  mutate(regularity_score = regularity_score/35)
```

>>>>

MOVE TO R SCRIPT!

@@

```
```{r}
youtube <- youtube %>% 
  mutate(
    daily = ifelse(
      days == "Every day",
      "Every Day",
      "Not Every Day"
    )
  ) %>% 
  mutate(Ptime = as.numeric(Ptime))
```

```{r}
youtube <- youtube %>% 
  mutate(
    race = ifelse(
      race_ethnicity == "White",
      "White",
      "POC"
    )
  )
```

```{r recoding}
youtube <- youtube %>% 
  mutate(
    across(c(`homophily_appear_1`, `homophily_appear_2`, `homophily_appear_3`, `homophily_appear_4`, `homophily_appear_5`, `homophily_behave_1`, `homophily_behave_2`, `homophily_behave_3`, `homophily_behave_4`, `homophily_behave_6`, parasocial_1, parasocial_2, parasocial_3, parasocial_4, parasocial_5),
           ~ recode (.,
             "Really disagree" = 1,
             "Disagree" = 2,
             "I don't know" = 3,
             "Agree" = 4,
             "Really agree" = 5
           ))) %>% 
  mutate(
    across(c(malleable_1, malleable_2, malleable_3, malleable_4),
           ~ recode(.,
             "Really disagree" = 1,
             "Disagree" = 2,
             "Neither agree nor disagree" = 3,
             "Agree" = 4,
             "Really agree" = 5
           ))) %>%  
  mutate(
    across(c(regularities_1, regularities_2, regularities_3, regularities_4, regularities_5, regularities_6, regularities_7),
           ~ recode(.,
             "Really disagree" = 1,
             "Disagree" = 2,
             "Neither agree nor disagree" = 3,
             "Agree" = 4,
             "Really  agree" = 5
           ))) %>%  
  select(-c(homophily_behave_5))
```

@@

```{r birthdays}
date_today <- Sys.Date()

birthday <- function(df, column_name, date_today) {
  df <- df %>%
    mutate(
      # Convert valid date strings to Date format
      bday_date = if_else(
        grepl("^\\d{2}/\\d{2}/\\d{4}$", .[[column_name]]), 
        as.Date(.[[column_name]], format = "%m/%d/%Y"), 
        NA_Date_
      ),

      # Extract last 4 characters for non-date values
      bday_year = if_else(
        is.na(bday_date), 
        as.numeric(substr(.[[column_name]], nchar(.[[column_name]]) - 3, nchar(.[[column_name]]))), 
        NA_real_
      ),

      # Calculate age based on actual date or extracted year
      age = if_else(
        !is.na(bday_date), 
        as.numeric(difftime(date_today, bday_date, units = "days")) / 365.25, 
        2025 - bday_year
      )
    ) %>%
    select(-bday_date, -bday_year)  # Remove intermediate columns

  return(df)
}

youtube <- birthday(youtube, "bday", date_today)

youtube <- youtube %>% 
  mutate(
    in_range = case_when(
      age < 14 ~ TRUE,
      age >= 14 ~ FALSE
    )
  )
```

@@

# Parasocial relationship scores (each block separately, then aggregate)
youtube <- youtube %>% 
  # homophily-appear -- total possible score = 20
  mutate(h_appear_score = rowSums(across(homophily_appear_1:homophily_appear_5))) %>% 
  # homophily-behave -- total possible score = 20
  mutate(h_behave_score = rowSums(across(homophily_behave_1:homophily_behave_6))) %>% 
  # parasocial -- total possible score = 20
  mutate(parasocial_score = rowSums(across(parasocial_1:parasocial_5))) %>% 
  #Composite scores
  mutate(composite = rowSums(across(h_appear_score:parasocial_score))) %>% 
  # Proportion scores
  mutate(h_appear_score = h_appear_score/20) %>%
  mutate(h_behave_score = h_behave_score/20) %>%
  mutate(parasocial_score = parasocial_score/20) %>%
  mutate(composite = composite/60)

# Racial regularities score (behavior) -- total possible score = 35
youtube <- youtube %>% 
  # Reverse coded items
  mutate(across(c(regularities_3, regularities_5, regularities_7), ~ 6 - .)) %>% 
  # Score
  mutate(regularity_score = rowSums(across(regularities_1:regularities_7))) %>% 
  mutate(regularity_score = regularity_score/35)
```
